Project assignment - Tahoe-LAFS with SHA-3 candidates

### 2010-10-06 paper/main.tex
Added more layout, and a problem description
Updated BibTeX use and the Makefile

\documentclass[english,12pt,a4paper]{report}
%[twoside] ?
\usepackage[T1]{fontenc} % In case we want special characters
\usepackage[utf8]{inputenc} % We are all writing in UTF-8

\usepackage{graphicx} % We _may_ use images
% Lager automagisk interne lenker i dokumentet.
\usepackage{hyperref} % Internal links is nice
\hypersetup{pdfborder=0 0 0} % ..especially without red borders

\author{Eirik Haver and Pål Ruud}
\title{Project assignment - Tahoe-LAFS with SHA-3 candidates}
\date{\today}

@@

\include{title}

\section*{Summary}

\section*{Foreword}

\tableofcontents
\newpage

\listoftables
\listoffigures

% Acronyms?

\chapter{SHA-3 in Tahoe-LAFS}

\section{Introduction}

\section{The candiates}

>>>>

\documentclass[english,12pt,a4paper]{book}
\usepackage[T1]{fontenc} % In case we want special characters
\usepackage[utf8]{inputenc} % We are all writing in UTF-8

\usepackage{appendix} % Fixes formatting of appendicies
\usepackage{graphicx} % We *may* use images
\usepackage{hyperref} % Internal and external links is nice
\hypersetup{pdfborder=0 0 0} % ..especially without red borders

% We need this to make it easier to ensure we start chapters on odd pages.
\newcommand{\ensureodd}{
    \newpage
%    \thispagestyle{empty}
    \mbox{}
}

\author{Eirik Haver \and Pål Ruud}
\title{Project assignment - Tahoe-LAFS with SHA-3 candidates}
\date{\today}

@@

\include{title}
\pagestyle{empty}

\chapter*{Abstract}
\addcontentsline{toc}{chapter}{Abstract}
\pagestyle{plain}
\pagenumbering{Roman}
\setcounter{page}{1}

\chapter*{Preface}
\addcontentsline{toc}{chapter}{Preface}

\tableofcontents

\addcontentsline{toc}{chapter}{\listfigurename} % Manual, because report style
\listoffigures

\addcontentsline{toc}{chapter}{\listtablename}
\listoftables

\chapter*{Acronyms}
\addcontentsline{toc}{chapter}{Acronyms}

% Insert acronyms here

\chapter{Introduction}
\pagenumbering{arabic}
\setcounter{page}{1}

Thorough problem description

\section{Method}

Technical procedure, Cython, two persons, test environment, how we test,
GitHub?

\section{Scope and objectives}

Should we include this?

\section{Outline}

What follows in this document, chapter by chapter

\chapter{Background technologies}
% Find new and better title

\section{NIST SHA-3}

Hash functions, NIST Comptetition, Candidates, SuperCop?

\section{Tahoe-LAFS}

What is it, how/where are hash functions used, Python, pycryptopp

\section{Python bindings using Cython}

What is it, how, why, alternatives?

\chapter{Procedure}

TODO: We have to figure out a new title
Keywords: Python bindings in detail, unit tests, using it in Tahoe-LAFS

A bit more technical description of how we tested the candidates in Tahoe-LAFS

Limitations/assumptions

Optimized candidates.

\chapter{Results}

What is tested and what is not tested?

tables, graphs?

\chapter{Discussion}

What could have been done differently?

Compare results with general (supercop) results.

Optimized candidates.

\cite{nistround2}

\chapter{Conclusion}

A somewhat short conclusion summing up results and discussion

\section{Future work}

New SHA-3 capability in Tahoe-LAFS (GSOC ref) to get our code to trunk

% BibTeX bibliography lives in external file
\bibliographystyle{plain}
\bibliography{ref_sha3}

\appendix
\appendixpage
\addappheadtotoc

% Use ordinary \chapters from here on..
